Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-05 Documents/Paper/ms.tex
Logz and H

\begin{figure}
\begin{center}
\includegraphics{pgm.pdf}
\caption{\it A probabilistic graphical model (PGM) depicting the kind
of model discussed in this paper. Produced using daft ({\tt daft-pgm.org}).
The number, $N$, of components in the model is an unknown parameter, as are the
properties of the components. The data depends on the properties of the components.
Note that it is possible (and common) to have other parameters in the model
that point directly to the data. However, we have omitted such parameters
for simplicity.
\label{fig:pgm}}
\end{center}
\end{figure}

@@

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -1410.8$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 29.7 nats.

>>>>

\begin{figure}
\begin{center}
\includegraphics{pgm.pdf}
\caption{A probabilistic graphical model (PGM) depicting the kind
of model discussed in this paper. Produced using daft ({\tt daft-pgm.org}).
The number, $N$, of components in the model is an unknown parameter, as are the
properties of the components. The data depends on the properties of the components.
Note that it is possible (and common) to have other parameters in the model
that point directly to the data. However, we have omitted such parameters
for simplicity.
\label{fig:pgm}}
\end{center}
\end{figure}

@@

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -771.8$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 39.8 nats.
